---
title: "hw 8  Calculating probabilities for the beta distribution"
output:
  pdf_document: default
  html_notebook: default
---



'rv' means *random variable*.  

Expected value of a beta rv:  if $X \sim beta(\alpha, \beta)$, then the expected value of $X$ is given by $E[X] = \frac{\alpha}{\alpha + \beta}$.  The expected value is the same thing as the mean. 

Variance of a beta rv:  *add this yourself*

Standard deviation of beta rv: *add this yourself*

Probability density function of a beta rv:  if $X \sim beta(\alpha, \beta)$, then the pdf of $X$ is given by $$f(x) = add \ \ this \ yourself $$

### Some beta rvs
The questions below refer to these 5 random variables: 
$$V \sim beta(2,3)$$



$$W \sim beta(18,6)$$
$$X \sim beta(1,1)$$



$$Y \sim beta(2,1)$$


$$Z \sim beta(4,4)$$


(@) Which rv's are symmetrically distributed? 
answer: z, x because they have alpha = beta

(@) Which one(s) is(are) skewed right? 
answer: V bc 3 > 2 (you can use E[v] = 2/2 + 3 = 2/5, if the probability is greater than 5 is skewed to the right)

(@) Which one is uniformly distributed?
answer: x because alpha and beta equal 1 therefore its uniform.

problem 4(@) Find the mean, variance, and standard deviation or each rv.  Store and display your results in a 5x4 tibble called `fivebetas`.  Use `tribble()` (part of the `tidyverse` package) to make the tibble. 

```{r}
fivebetas <- tribble(
  ~rvs, ~mean, ~variance, ~sd,
  "v",.4, .19,.4358,
  "w",.75, .1797,.4239,
  "x",.5, .1428,.3778,
  "y",.67, .1538,.3921,
  "z",.5, .2191,.4680
)
fivebetas
```


problem 5. (@) Find the probability that each of the rvs is greater than .5.  Store and display your results in a 5x2 tibble called `Pgreaterthanpointfive`.  Don't use `tribble()` this time.  Just use `tibble()`.  Make a plot to tell the story for each rv. 

```{r}

```


problem 6 - (@) Find $P(X < .25 \ | \ X < .5)$ and make a plot to tell the story.

```{r}
x <- pbeta(.25,1,1)/pbeta(.5, 1, 1)
x
xvec <- seq(-1,2, by=.001)
yvec <- dbeta(xvec, 1,1)
plot(xvec, yvec, type = 'l')
#abline(h=0, col=5) 
#points(.5, 0,pch=19)
lines(c(.5,.5), c(0, 1), col=1) # vertical line that's just right
#answer goes on the right
text(.2,.5,'.5')

```

(@) problem 7 Do the same thing for $Y$.

```{r}

y <-  pbeta(.25,2,1)/pbeta(.5, 2, 1)
y
#plot for that problem
#plot pdf, slice itm color it, label it
xvec <- seq(-2,5,by=.1)
yvec <- dbeta(xvec, 2,1)
plot(xvec, yvec, type = 'l')
#abline(h=0, col=5) ; abline(v=0,col=5)
#dot at x = .5
#runs a line through point at .5
#abline(v =.5)
#lines(c(.5,.5), c(0, dbeta(.5, 2,3)), col=5) # vertical line that's just right
#answer goes on the right
text(.6,.5,'.3125')
```

(@) problem 8 Find $P(Z > .8 \ | \ Z < .6)$  For this one it's enough to just explain your answer.  You don't have to use R or make a plot.  

Answer: 0 since there is no overlapping probabilities for z >.8 and z < .6.


(@) problem 9 Find $P(V > .7 \ | \ V > .6)$ and make a plot to tell the story.
answer: .467

```{r}
v <- (1 - pbeta(.7, 2, 3))/(1 - pbeta(.6, 2, 3))
v
xvec <- seq(0,1,by=.01)
yvec <- dbeta(xvec, 2,3)
plot(xvec, yvec, type = 'l')
#abline(h=0, col=5) ; abline(v=0,col=5)
#abline(v =.5)
lines(c(.6,.6), c(0, 1.2), col=1) # vertical line that's just right
#answer goes on the right
text(.7,.4,'.467')


```


(@) problem 10 Find $P(V > .6 \ | \ .3 < V < .7)$ and make a plot to tell the story.

```{r}

v <- (1 - pbeta(.6,2,3))/(pbeta(.7,2,3) - pbeta(.3,2,3))
xvec <- seq(0,1,by=.01)
yvec <- dbeta(xvec, 2,3)
plot(xvec, yvec, type = 'l')
lines(c(.6,.6), c(-1, 1.18), col=1) 
lines(c(.7,.7), c(-1, .78), col=1)
text(.65,.4,'.315')

```


(@) problem 11 Find $P(V > .7 \ | \ V > .6\ \ or \ V < .4)$ and make a plot to tell the story.

```{r}
g <- (1 - pbeta(.7,2,3))/((1-pbeta(.6,2,3)) + (pbeta(.4,2,3))) 
g
xvec <- seq(0,1,by=.01) 
yvec <- dbeta(xvec, 2,3)
plot(xvec, yvec, type = 'l')
lines(c(.6,.6), c(-1, 1.18), col=1) 
lines(c(.4,.4), c(-1, 1.73), col=1)
lines(c(.7,.7), c(-1, .78), col=1)
text(.65,.4,'.118')

```





