---
title: "quizlet which comes between hw8 and quiz3"
output: html_notebook
---

Submit your .Rmd on Blackbaord AND submit this paper in class.  Write your answers on this paper.  There are 100 points, broken down like this:  

 Problem | 1 | 2 | 3 | 4 | 5 | 6 | 7 
 --------|---|---|---|---|---|---|--- 
 Point
 s | 20 | 10 | 10 | 10 | 10 | 20 | 20 
 
#### Problem 1
Suppose $W \sim beta(3.5, 2.5)$.  Find $P(W \leq .65)$ and $P(W > .65)$. 
```{r}
pbeta(.65, 3.5, 2.5)
1 - pbeta(.65, 3.5, 2.5)
```
#### Problem 2
Suppose $Y \sim beta(2,1)$.  Find $P(Y > .125)$. 
```{r}
1 - pbeta(.125, 2, 1)
```
#### Problem 3
Suppose $X \sim beta(.8, .8)$.  Find $P(.3 < X < .7)$. 
```{r}
pbeta(.7,.8,.8) - pbeta(.3, .8,.8) 
```
#### Problem 4
Suppose $V \sim beta(4,4)$.  Find $P(V > .5)$. 
```{r}
1 - pbeta(.5, 4, 4)
```
#### Problem 5
Use $V$ from the previous problem.  Find $P(V \leq .75 | V > .5)$. 
```{r}
(pbeta(.75,4,4) - pbeta(.5,4,4))/ pbeta(.5,4,4) 
```
#### Problem 6
Pick any two problems from above and make a sketch on this paper to tell the story. 

<br>
<br>
<br> 
<br>
<br>
<br> 
#### Problem 7
Pick any two problems from above and make a plot in R to tell the story. 
```{r}

#Plot $P(Y > .125)$. 

1 - pbeta(.125, 2, 1)
v <- 1 - pbeta(.125, 2, 1)
#plot for that problem
#plot pdf, slice itm color it, label it
xvec <- seq(0,1,by=.10)
yvec <- dbeta(xvec, 2,1)
plot(xvec, yvec, type = 'l')
abline(h=0, col=5) ; abline(v=0,col=5)
#dot at x = .5
points(.125, 0,pch=19)
#runs a line through point at .5
#abline(v =.5)
#answer goes on the right
text(.6,.5,'.125')


#Plot $P(V > .5)$.

v <- 1 - pbeta(.5,4,4)
#plot for that problem
#plot pdf, slice itm color it, label it
xvec <- seq(0,1,by=.01)
yvec <- dbeta(xvec, 4,4)
plot(xvec, yvec, type = 'l')
abline(h=0, col=5) ; abline(v=0,col=5)
#dot at x = .5
points(.5, 0,pch=19)
#runs a line through point at .5
#abline(v =.5)
lines(c(.5,.5), c(0, dbeta(.5, 4,4)), col=5) # vertical line that's just right
#answer goes on the right
text(.6,.5,'.5')


```

