---
title: 'hw9: Shazam data import'
author: 'Marcus Arzadon, Gabriel Ixcolin, Sharrah Allen, Than La, Azfar Vahidy, Francisco Ramirez'
output:
  pdf_document: default
  html_notebook: default
---

##### Resources
This hw requires the packages `tidyverse` and `readxl`.  Maybe more.   Data files are **hw7.stageleft.xlsx** and **Stage_Right_Project.xlsx**.  Code we wrote in class last week (Week 13) will help.  

```{r}
library(tidyverse)
library(readxl)
```


##### 1.  
Import the first tab from **hw7.stageleft.xlsx** and call the new data.frame `shazam.dat`.  

```{r}
shazam.dat <- read_xlsx('hw7.stageleft.xlsx',sheet=1)
shazam.dat$Group_Member[shazam.dat$Group_Member == "Thanh La"] = "La"
shazam.dat$Group_Member[shazam.dat$Group_Member == "Fransisco"] = "Ramirez"
shazam.dat$Group_Member[shazam.dat$Group_Member == "Marcus Arzadon"] = "Arzadon"
shazam.dat$Group_Member[shazam.dat$Group_Member == "Azfar Vahidy"] = "Vahidy"
shazam.dat$Group_Member[shazam.dat$Group_Member == "Sharrah Allen"] = "Allen"
shazam.dat$Group_Member[shazam.dat$Group_Member == "Gabriela Ixcolin"] = "Ixcolin"

names(shazam.dat)[2] = "LastName"
names(shazam.dat)[1] = "GroupName"
names(shazam.dat)[6] = "SongStartTime"
names(shazam.dat)[7] = "SongStopTime"
names(shazam.dat)[8] = "ShazamSong"
names(shazam.dat)[9] = "ShazamArtist"
names(shazam.dat)[10] = "Correct"

```


##### 2. 
The original instructions from hw7 are pasted below.  Review these and decide as a group whether to make any changes to `shazam.dat`.  We decided last week to definitely keep the GENRE column that appears in the Stage Left hw7.  Include a  bulleted list in your .Rmd describing each column in your final version of `shazam.dat`.   This is the place to describe any changes you are making to the raw version of `shazam.dat`.  The final version of `shazam.dat` will get used in the next step.  

- Group_Name: the group that the entry/ member belongs to
- Group_Member: name of the person who made the entry
- Song: song of that is being shazamed
- Artist: the correct/ original artist of the song
- Genre: category/ genre of the song
- Song Start Time: start of shazam in time of the song
- Song Stop Time: time in the song that shazam "got" the song
- Shazam Song: Song that shazam suggests you are listening to
- Shazam Artist: Artist shazam believes is performing/ created the song
- Correct?: did shazam get it right or wrong

**Changes**
- create a col called duration that measures seconds shazam took to solve the song
- Change group members to lastname. will hold only the last name of the person's last name who made the entry

```{r}
shazam.dat <- shazam.dat %>% mutate(Duration = as.integer(difftime(SongStopTime,SongStartTime,units="mins"))) %>% select(-c(SongStopTime, SongStartTime))
```

```{r}
shazam.dat <- shazam.dat %>% mutate(ID = 1:nrow(shazam.dat)) %>%  select(ID,everything())
shazam.dat
```


##### 3. 
Now consider the Stage Right hw7 data in **Stage_Right_Project.xlsx**.  Import each tab of this spreadsheet and add its data to `shazam.dat`.  That will happen with a command like `shazam.dat <- rbind(shazam.dat, newtab)`.  Before you run this you'll have to make the columns of `newtab` match the columns of `shazam.dat`.  That will take some work and that's the point of this hw.    

```{r}
path <- 'Stage_Right_Project.xlsx'
(sheet1 <- read_xlsx(path,sheet=1))
rowcount <- nrow(sheet1)


template <- shazam.dat %>% head(15)
template <- template[-c(seq(1,15)),]
dim(template)
template[1:rowcount,1:ncol(template)] <- NA
head(template)
```

```{r}
excel_sheets(path)[1]
```


```{r}
template$ID<- sheet1$Labels
template$GroupName<- "Stage Right"
template$LastName<- "Ali"
template$Song<- sheet1$Song
template$Artist<- sheet1$Artist
template$Genre<- NA
template$ShazamSong<- sheet1$`Shazam Song`
template$ShazamArtist<- sheet1$`Shazam Artist`
template$Duration<- sheet1$`Time(secs)`
condition1 <- sheet1$Song == sheet1$`Shazam Song`
condition2 <- sheet1$Artist == sheet1$`Shazam Artist`
template$Correct <- ifelse(condition1 & condition2 ,'Yes','No')
rbind(shazam.dat,template) -> shazam.dat
shazam.dat
```
Repeat the process to add the next sheet to `shazam.dat`
```{r}
path <- 'Stage_Right_Project.xlsx'
(sheet2 <- read_xlsx(path,sheet=2))
rowcount <- nrow(sheet2)


template <- shazam.dat %>% head(15)
template <- template[-c(seq(1,15)),]
dim(template)
template[1:rowcount,1:ncol(template)] <- NA
head(template)
```
```{r}
template$ID<- NA
template$GroupName<- "Stage Right"
template$LastName<- excel_sheets('Stage_Right_Project.xlsx')[2]
template$Song<- sheet2$song_searched
template$Artist<- sheet2$artist_searched
template$Genre<- NA
template$ShazamSong<- sheet2$song_returned
template$ShazamArtist<- sheet2$artist_returned
template$Duration<- NA
condition1 <- sheet2$song_searched == sheet2$song_returned
condition2 <- sheet2$artist_searched == sheet2$artist_returned
template$Correct <- ifelse(condition1 & condition2 ,'Yes','No')
rbind(shazam.dat,template) -> shazam.dat
shazam.dat
```

```{r}
path <- 'Stage_Right_Project.xlsx'
(sheet3 <- read_xlsx(path,sheet=3))
rowcount <- nrow(sheet3)


template <- shazam.dat %>% head(15)
template <- template[-c(seq(1,15)),]
dim(template)
template[1:rowcount,1:ncol(template)] <- NA
head(template)
```
```{r}
as.integer(substr(sheet3$`Time  Duration`,1,1))
```
```{r}
# add data from sheet3 to new template
template$GroupName <- "Stage Right"
template$LastName <- excel_sheets('Stage_Right_Project.xlsx')[3]
template$Song <- sheet3$Song
template$Artist <- sheet3$Artist
template$Genre <- sheet3$Category
# since there's no incorrect responses, we can re-use the Artist and Song columns 
template$ShazamSong <- sheet3$Song
template$ShazamArtist <- sheet3$Artist
template$Correct <- sheet3$`Returned or Not`
template$Duration <- as.integer(substr(sheet3$`Time  Duration`,1,1))
#add template to shazam.dat
rbind(shazam.dat,template) -> shazam.dat
```
```{r}
shazam.dat
```

```{r}
path <- 'Stage_Right_Project.xlsx'
(sheet4 <- read_xlsx(path,sheet=4))
rowcount <- nrow(sheet4)


template <- shazam.dat %>% head(15)
template <- template[-c(seq(1,15)),]
dim(template)
template[1:rowcount,1:ncol(template)] <- NA
head(template)
```
```{r}
template$ID<- sheet4$`song label`
template$GroupName<- "Stage Right"
template$LastName<- excel_sheets('Stage_Right_Project.xlsx')[4]
template$Song<- sheet4$Song
template$Artist<- sheet4$Artist
template$Genre<- NA
template$ShazamSong<- NA
template$ShazamArtist<- NA
template$Duration<- NA
template$Correct <- NA
rbind(shazam.dat,template) -> shazam.dat
shazam.dat
```
```{r}
path <- 'Stage_Right_Project.xlsx'
(sheet5 <- read_xlsx(path,sheet=5))
rowcount <- nrow(sheet5)


template <- shazam.dat %>% head(15)
template <- template[-c(seq(1,15)),]
dim(template)
template[1:rowcount,1:ncol(template)] <- NA
head(template)
```
```{r}
template$ID<- sheet5$...1
template$GroupName<- "Stage Right"
template$LastName<- excel_sheets('Stage_Right_Project.xlsx')[5]
template$Song<- sheet5$Song
template$Artist<- sheet5$Artist
template$Genre<- NA
template$ShazamSong<- NA
template$ShazamArtist<- NA
template$Duration<- NA
template$Correct <- ifelse(sheet5$Result == 1,"Yes","No")
rbind(shazam.dat,template) -> shazam.dat
shazam.dat
```
```{r}
path <- 'Stage_Right_Project.xlsx'
(sheet6 <- read_xlsx(path,sheet=6))
rowcount <- nrow(sheet6)


template <- shazam.dat %>% head(15)
template <- template[-c(seq(1,15)),]
dim(template)
template[1:rowcount,1:ncol(template)] <- NA
head(template)
```
```{r}
template$ID<- sheet6$song
template$GroupName<- "Stage Right"
template$LastName<- excel_sheets('Stage_Right_Project.xlsx')[6]
template$Song<- sheet6$`correct song`
template$Artist<- sheet6$Artist
template$Genre<- NA
template$ShazamSong<- NA
template$ShazamArtist<- NA
template$Duration<- sheet6$`time to discover (sec)`
template$Correct <- ifelse(sheet6$`correct song` == sheet6$`returned song`,"Yes","No")
rbind(shazam.dat,template) -> shazam.dat
shazam.dat
```
```{r}
path <- 'Stage_Right_Project.xlsx'
(sheet7 <- read_xlsx(path,sheet=7))
rowcount <- nrow(sheet7)


template <- shazam.dat %>% head(15)
template <- template[-c(seq(1,15)),]
dim(template)
template[1:rowcount,1:ncol(template)] <- NA
head(template)
```
```{r}
template$ID<- sheet7$Label
template$GroupName<- "Stage Right"
template$LastName<- excel_sheets('Stage_Right_Project.xlsx')[7]
template$Song<- sheet7$Chosen_SongName
template$Artist<- sheet7$Chosen_Artist
template$Genre<- NA
template$ShazamSong<- sheet7$Shazaam_SongName
template$ShazamArtist<- sheet7$Shazaam_Artist
template$Duration<- sheet7$Time_sec
condition1<- sheet7$Chosen_SongName == sheet7$Shazaam_SongName
condition2<- sheet7$Chosen_Artist == sheet7$Shazaam_Artist
template$Correct <- ifelse(condition1 & condition2,"Yes","No")
rbind(shazam.dat,template) -> shazam.dat
shazam.dat
```






##### Original specs from hw7
Select a random song, play it for Shazam, give Shazam 10 seconds to respond, record its guess for the song (or record NA if Shazam failed to come back in 10 seconds).  Performing the experiment generates an outcome.  Each student should perform the experiment 15 times. 

Include the name of your hw group, your last name, a number to label your songs (you can use 1,2,3,.... or whatever), the date and time of the experiment, the song and artist that you played, the song and artist returned by Shazam (or NA's if Shazam fails), was Shazam right or wrong, etc.  

Etc. means include more variables if you want.  Like maybe how long it took for Shazam to return its answer, or what part of the song you played, or what category of music was the song.  







