---
title: "Week7 Tuesday"
output: html_notebook
---

```{r }
#install.packages("palmerpenguins")
#install.packages('dplyr')
#install.packages('magrittr')
#install.packages('sqldf')

rm(penguins)
library(palmerpenguins)  # for data
library(dplyr)
library(magrittr) # for the pipe
library(sqldf)  # really just a function called sqldf()

penguins$species <- as.character(penguins$species)  # converting factors to character
penguins$island <- as.character(penguins$island)
penguins$sex <- as.character(penguins$sex)

# modify penguins by removing rows that contain NA
penguins <- na.omit(penguins) 
# questions below refer to his modified version of penguins
```

# SQL is old, OLD
Many versions exist, not all free, we are using SQLite when we call `sqldf()` without any extra arguments  (other versions of SQL include mySQL, SQLServer, msSQL, postgreSQL, etc. )

```{r}
# make a character string with a query like the ones on the whiteboard
qstr <- 'Select * from penguins where body_mass_g < 3000'
sqldf(qstr)

qstr <- 'Select * from penguins where body_mass_g < 3000' 
```

So it works.  Now run queries from whiteboard. 

TONIGHT:  run help(paste) and look at examples for all the things you can do!

```{r}
qstr1 <- 'Select island, species, year, max(bill_length_mm) as maxbill'
qstr2 <- 'from penguins '
qstr3 <- 'where sex = "male"'
qstr4 <- 'group by island, species, year'
qstr <- paste(qstr1, qstr2, qstr3, qstr4)
qstr

sqldf(qstr)

help(paste)

```
Now the one with `top5Adelie` and `bottom5Adelie`
```{r}
qstr <- 'SELECT * FROM penguins WHERE species = "Adelie" ORDER BY bill_length_mm DESC LIMIT 5'

(top5Adelie <- sqldf(qstr))

qstr <- 'SELECT * FROM penguins WHERE species = "Adelie" ORDER BY bill_length_mm  LIMIT 5'
(bottom5Adelie <- sqldf(qstr))
```

# counting records in SQL

use the same code again ...

```{r}
qstr <- 'SELECT COUNT(*) FROM penguins WHERE species = "Chinstrap" '
sqldf(qstr)
```
you can count in combinatin with group by,
like we did in dplyr using n()
```{r}
qstr1 <- 'Select island, species, year, max(bill_length_mm) as maxbill, count(*) as n_penguins'
qstr2 <- 'from penguins '
qstr3 <- 'where sex = "male"'
qstr4 <- 'group by island, species, year'
qstr <- paste(qstr1, qstr2, qstr3, qstr4)
qstr

sqldf(qstr)
```

