---
title: "R Notebook"
output: html_notebook
---

```{r}
install.packages("tidyverse")
library(tidyverse)
library(ggplot2)

```


In the last 36 months, I have traveled to several cities all over the U.S. The trips budget are often affected by location, time traveling,number of people traveling and duration of the trip. I am planning another trip for next year and I want to see if my previous trips could help me decifer what would be the best place to go to. 

I begin by importing the data. On any given trip there are three main expenses: flight ticket, housing, and transportation. Flight ticket is diretly affected by when I'm traveling the day I'm leaving and the day I'm returning. The following chart compares the follwing information.

```{r}
mpg
g <- mpg$manufacturer
ggplot(data = mpg) + 
         geom_point(mapping = aes(x = displ, y = hwy))
```


```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = class))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~class, nrow = 2)
```

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(~drv ~ cyl)
```


```{r}
month <- c('september','january','Dicemeber')
day_of_departure <- c('monday','sunday','saturday')
day_of_return <- c('friday','monday','sunday')
```

Housing is directly affected by time of year traveling, number of days staying, and location traveling to. Busier seasons are often hollidays and places are more expensive in those times. The following information compares the days traveling, location traveling to, and time of year traveling.

```{r}
month <- c('september','january','Dicemeber')
day_of_departure <- c('monday','sunday','saturday')
day_of_return <- c('friday','monday','sunday')
```

The last biggest expense is the transportation. For the most of the



```{r}
ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy, linetype = drv))
```
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(mapping = aes(x = displ, y = hwy))
```
```{r}
ggplot(data = diamonds) + 

    stat_count(mapping = aes(x = cut))
```
```{r}
ggplot(data = diamonds) + 
  stat_summary(mapping = aes(x = cut, y = depth),
               fun.min = min,
               fun.max = max,
               fun = median
               )

ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, colour = cut))

ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut, fill = clarity))

ggplot(data = diamonds, mapping = aes(x = cut, fill = clarity)) +
  geom_bar(alpha = 1/5, position = "identity")
  
```

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), position = "jitter")
```

```{r}
library(nycflights13)
library(tidyverse)

filter(flights, month == 1, day == 1)
jan1 <- filter(flights, month == 1, day == 1)

```

