---
title: "R Notebook"
output: html_notebook
---

This data contains information about user performance's when tracking their workouts. The dataset has the following files:

DailyActivity
DailyCalories
DailyIntensities
DailySteps



The questions we want to answer:

1) What are some trends we can spot?
2) Does certain types of excercises lead to higher levels of calorie burning
3) How can we use this information for marketing purposes? 


GATHERING THE DATA 

The first step is getting the data. To do this we will use read_csv to pass the path through it. 

```{r}
install.packages("reshape2")
library(tidyverse)
library(reshape2)
daily_activity <- read_csv("dailyActivity_merged.csv")
daily_calories <- read_csv("dailyCalories_merged.csv")
daily_intensities <- read_csv("dailyIntensities_merged.csv")
daily_steps <- read_csv("dailySteps_merged.csv")
heart_rate <- read_csv("heartrate_seconds_merged.csv")
hourly_Calories <- read_csv("hourlyCalories_merged.csv")
hourly_intensities <- read_csv("hourlyIntensities_merged.csv")
hourly_steps1 <- read_csv("hourlySteps_merged.csv")
sleepday <- read_csv("sleepDay_merged.csv")

```



```{r}
n_distinct(daily_activity$Id)
n_distinct(daily_calories$Id)
n_distinct(daily_intensities$Id)
n_distinct(daily_steps$Id)
n_distinct(hourly_intensities$Id)
n_distinct(hourly_steps1$Id)
n_distinct(sleepday$Id)
```

```{r}
sum(duplicated(sleepday))
sum(duplicated(hourly_steps))
```


CLEANING THE DATA


I want to remove any duplicate values since that will cause errors in our analysis. To do this we use drop_na(). 

```{r}
hourly_steps <- hourly_steps %>%
  distinct() %>%
  drop_na()

hourly_intensities <- hourly_intensities %>%
  distinct() %>%
  drop_na()

daily_activity <- daily_activity %>%
  distinct() %>%
  drop_na()

hourly_intensities1 <- hourly_intensities1 %>% 
  distinct() %>% 
  drop_na()

daily_sleep <- sleepday %>% 
  distinct() %>% 
  drop_na()
```


We want to format our dates to make easier to work with. To do this we use the format function along with the as.Date to make those changes. I want to format the date time and add a new column called "Day_of_the_week" to the data. 

```{r}
#Change the date format and add a column with day of the week
daily_activity$ActivityDate<- as.POSIXct(daily_activity$ActivityDate, format= "%m/%d/%Y")
daily_activity<-transform(daily_activity,Day_of_the_week=weekdays(ActivityDate))

daily_intensities$ActivityDay <- as.POSIXct(daily_intensities$ActivityDay, format= "%m/%d/%Y")
daily_intensities <- transform(daily_intensities, Day_of_the_week = weekdays(ActivityDay))

daily_steps$ActivityDay <- as.POSIXct(daily_steps$ActivityDay, format= "%m/%d/%Y")
daily_steps <- transform(daily_steps, Day_of_the_week = weekdays(ActivityDay))


hourly_Calories$ActivityHour <- as.POSIXct(hourly_Calories$ActivityHour, format= "%m/%d/%Y")
hourly_Calories <- transform(hourly_Calories, Day_of_the_week = weekdays(ActivityHour))

hourly_intensities$ActivityHour <- as.POSIXct(hourly_intensities$ActivityHour, format= "%m/%d/%Y %I:%M:%S %p",tz=Sys.timezone()) 
hourly_intensities <- transform(hourly_intensities, Day_of_the_week = weekdays(ActivityHour))

hourly_steps <- hourly_steps1 %>% 
  rename(date_time = ActivityHour) %>% 
  mutate(date_time = as.POSIXct(date_time,format ="%m/%d/%Y %I:%M:%S %p" , tz=Sys.timezone()))
hourly_steps <- transform(hourly_steps,Day_of_the_week = weekdays(date_time))

daily_sleep
daily_sleep <- daily_sleep %>%
  rename(date = SleepDay) %>%
  mutate(date = as.POSIXct(date,format ="%m/%d/%Y %I:%M:%S %p" , tz=Sys.timezone()))


``` 

I notice that the data tracks either day, hours, or minutes. Since I don't want to work with many too many datasets I'll combine them using merge. 

```{r}
#joins daily_activity and daily calories tables using Id and Calories
activity_calories = full_join(daily_activity, daily_calories, by= c("Id","Calories"))


#removes the last extra column from the table
activity_calories <- activity_calories[,-17]

#joins daily_intensities and daily steps tables using Id, AcitivityDay, and Day of the Week
daily_workout = full_join(daily_intensities, daily_steps, by=c("Id","ActivityDay","Day_of_the_week"))


daily_activity
daily_sleep
daily_activity_sleep <- merge(daily_activity, daily_sleep, by=c("id", "date"))
glimpse(daily_activity_sleep)
```

Analysis 



```{r}
summary_distance <- activity_calories %>% group_by(Day_of_the_week) %>% 
  summarise_at(c(LightActiveDistance= "LightActiveDistance", ModeratelyActiveDistance = "ModeratelyActiveDistance",VeryActiveDistance= "VeryActiveDistance"),mean) %>% arrange(desc(VeryActiveDistance))
summary_distance
```

This table demonstrates that on Wednesday had the highest activity distance. The lowest activity distance was reported on Friday. 


```{r}
summary_minutes <- activity_calories %>% group_by(Day_of_the_week) %>% 
  summarise_at(c(SedentaryMinutes = "SedentaryMinutes", LightlyActiveMinutes = "LightlyActiveMinutes", FairlyActiveMinutes = "FairlyActiveMinutes", VeryActiveMinutes = "VeryActiveMinutes"), mean) %>% arrange(desc(VeryActiveMinutes))
summary_minutes


summary_daily <- activity_calories %>% group_by(ActivityDate) %>% 
  summarise_at(c(SedentaryMinutes = "SedentaryMinutes", LightlyActiveMinutes = "LightlyActiveMinutes", FairlyActiveMinutes = "FairlyActiveMinutes", VeryActiveMinutes = "VeryActiveMinutes"), mean) %>% arrange(desc(VeryActiveMinutes))

summary_daily


```

The the most active time was during Saturday while the least active was Sunday. 

```{r}
summary_weekly <- activity_calories%>%
  group_by(Day_of_the_week)%>%
  summarise_at(c(avg_steps="TotalSteps",avg_distance="TotalDistance",avg_sedentary_mins="SedentaryMinutes",avg_calories="Calories",avg_active_mins="VeryActiveMinutes"),mean) %>% arrange(avg_calories)
summary_weekly

activity_calories

```

Sunday saw the most calories burned on average while Friday had the least amount of calories burned. 

```{r}
daily_activity %>% 
  group_by(TotalSteps, Calories) %>% 
  ggplot(aes(x = TotalSteps, y = Calories, color = Calories)) +
  geom_point() +
  geom_smooth() + 
  theme(legend.position = c(.8, .3),
        legend.spacing.y = unit(1, "mm"), 
        panel.border = element_rect(colour = "black", fill=NA),
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black")) +
  labs(title = 'Calories burned by total steps taken',
       y = 'Calories',
       x = 'Total Steps')
```
There seems to be a positive trend between the number of steps taken and the calories burned. 

```{r}
ggplot(hourly_steps) + geom_col(aes(x= reorder(Day_of_the_week,-StepTotal), y = StepTotal, fill=Day_of_the_week )) + labs(title="Calories by day of the week", x= "Day of the week", y="Calories burned") 
```
The day with the highest calories burned was Tuesday followed by wednesday. The least calories burned were on Sunday and Monday. 



```{r}


ggplot(hourly_intensities) + geom_col(aes(x= reorder(Day_of_the_week,-AverageIntensity), y = AverageIntensity, fill=Day_of_the_week )) + labs(title="Average Intensity by day of the week", x= "Day of the week", y="Intensity") 
```

Naturaly, the highest intensity was on Tuesday and Wednesday 

```{r}
ggplot(data= daily_activity,aes(x= Day_of_the_week,y=VeryActiveDistance )) + geom_boxplot()

```


```{r}

summary_daily
ggplot(summary_daily, aes(x=ActivityDate ,y=LightlyActiveMinutes)) + geom_line()
```



```{r}


mean_calories <- daily_activity %>% group_by(Day_of_the_week) %>% summarise(mean_calories = mean(Calories),mean_distance = mean(TotalDistance)) %>% arrange(mean_calories, mean_distance) 
mean_calories

```

Interestingly enough, Saturday is not the day that burns the most calories. It is Tuesday. I assume that user's activity is slightly more intense during the weekday. Additionally, Thursday
had the lowest calories burned even though it covered a longer distance than Sunday and Friday. This may be caused by the activity less intense on Thursday than it is on the other days. 



```{r}

newdata <- mutate(daily_activity, total_mints  = VeryActiveDistance + ModeratelyActiveDistance + LightlyActiveMinutes)

ggplot(data = newdata, aes(x= total_mints, y = Calories)) + geom_point(alpha= 0.7,shape="circle", size= 0.5, colour="blue") + geom_smooth(method = "lm") + labs(title = "Relation between Working out time vs. Calories burned")

```







